---
title: "Sample Fdk2R"
output:
  html_document:
    theme: united
    toc: yes
---

Sections:

* 1. Connection

* 2. Configuration (symbols, currencies, accounts)

* 3. Feed history  (bars and quotes)

* 4. Trades/Trade Reports


#1. Connection
Connect to TT Demo server:
ttConnect()

```{r}
options(warn=-1)
require(rClr)
require(FdkRLib)

ttConnect("", "", "")

```

#2. Configuration

Get symbol and currency data
```{r}
ttGetSymbolData()

ttGetCurrencyData()
```

#3. Feed history
<p>Get 10000 bars of EURUSD symbol:</p>
head(ttBarsHistory("EURUSD"))

```{r}
ttBarsHistory("EURUSD")
```

<p>Get 10000 bar quotes  of EURUSD symbol: </p>
bars = ttBarsQuotesHistory("EURUSD")

```{r}
ttBarsQuotesHistory("EURUSD")
```


Get quotes
```{r}

now <-as.POSIXct(Sys.time())
# 300 seconds from present
prevNow <-as.POSIXct(now-(300))

ttQuotesHistory("EURUSD", startTime = prevNow, endTime=now)
```

Get quotes L2
```{r}
now <-as.POSIXct(Sys.time())
# 1000 seconds from present
prevNow <-as.POSIXct(now-1000)

ttQuotesLevel2History('EURUSD', prevNow, now, depth=1)
```

#4. Trades/Trade Reports

Get trades of current account

```{r}
now <-as.POSIXct(Sys.time())
#120 hours = 5 x 24 x 3600 seconds before now
prevNow <-as.POSIXct(now-(5 * 24*3600))
ttTradeRecords(prevNow, now)
```

Trades in account:
```{r}
# Commented as it takes to long
ttConnect("tp.st.soft-fx.eu", "100066", "123qwe!")
head(ttTrades())
```
All trades
```{r}
# Commented as it takes to long
ttTradeRecordAll()
```
