---
title: "Sample Fdk2R"
output:
  html_document:
    toc: true
    theme: united
---

Sections
* 1. Connection
* 2. Configuration (symbols, currencies, accounts)
* 3. Feed history  (bars and quotes)
* 4. Trades/Trade Reports

#1. Connection
Connect to TT Demo server:
ttConnect()

```{r}
options(warn=-1)
require(rClr)
require(FdkRLib)
ttConnect()
```

#2. Configuration
Get symbol and currency data
```{r}
head(ttGetSymbolData())

head(ttGetCurrencyData())
```

#3. Feed history
<p>Get 10000 bars of EURUSD symbol:</p>
head(ttBars("EURUSD"))

```{r}
head(ttBars("EURUSD"))
```

<p>Get 10000 bar pairs of EURUSD symbol:</p>
bars = ttBarPairs("EURUSD")

```{r}
head(ttBarPairs("EURUSD"))
```


Get quotes
```{r}
head(ttQuotes("EURUSD", startTime= as.POSIXct(x = "2015-06-10", tz="UTC")))
```

Get trades of current account
```{r}
head(ttTrades())
```

Get quotes L2
```{r}
ttConnect("tp.st.soft-fx.eu", "100000", "123qwe!")
head(ttTrades())

now <-as.POSIXct(Sys.time())
prevNow <-as.POSIXct(Sys.time()-1000)

qt2= ttQuotesLevel2('EURUSD', prevNow, now)
head(qt2)
```

#4. Trades/Trade Reports



More functionality tested:

```{r}
ttConnect("tp.st.soft-fx.eu", "100000", "123qwe!")
trades = ttTrades()


bars = ttBars("EURUSD", barCount = 1000000)
barPairs = ttBarPairs('EURUSD')


qt = ttQuotes('EURUSD', startTime = prevNow, endTime=now)
quotesHistory <- ComputeQuoteHistory('EURUSD', startTime = prevNow, endTime=now, 1)

qt2= ttQuotesLevel2('EURUSD', prevNow, now)
```

